---
title: "R Notebook"
subtitle: "Read CSV files into dataframes, publish to a webpage" 
output:
  html_document:
    df_print: paged
---
Lifted a CSV from a Google spreadsheet, saved to the 'sheets'  folder in the workng directory. On examination decided to give the columns new, more intuitive. The content I require begins on the 3rd row, so will skip the first two rows. Code shown below.

```{r message=TRUE, warning=TRUE, include=FALSE, paged.print=FALSE, show_col_types=TRUE}

library(readr)
paidup <- read_csv("sheets/THTA-PaidUP-Sheet1.csv", 
        # skipping because of unwanted header and foll row
                   skip=2 ,
        col_names=c("PROPERTY","", "", "","UNIQUEID")
        )
# Put to print elsewhere
lmn = paidup[c(1, 5) ]
```

```{r message=TRUE, warning=TRUE, include=FALSE, paged.print=FALSE, show_col_types=TRUE}

library(readr)

smallaccs <- read_csv("sheets/smallAcc.csv")
# out to print elsewhere on page
smx = smallaccs[c(1, 2, 3)]
       
```


**The idea**: Read several CSV files into dataframes, embedding output into a Xaringan slideshow. 

## First: Getting ready to code 

I'm using RMarkdown, so several options are available but here's how it'll swing. Beneath is my prep game (requisites)

  1. An Rmarkdown Notebook. Invaluable for testing code away from project .Rmd or .R scripts  
  1. CVS data in local project folder. Placed like  "sheets/file.csv"  
  1. Install/update R's readr package (*part of the TidyVerse*)     

Since the dataframes will be embedded into a Xaringan slide (an HTML page) and today's exercise is solely about reading, customising and testing 'read.csv'.

But importantly will move on to 'read_csv' output as 

### Output. Paid up folks

```{r echo=FALSE}
print(lmn)

```


### Output Small hotels

```{r echo=TRUE}
print(smx)

```